---
title: "Untitled"
format: html
---

# Introduction
## About the data
This data set contains North Pole Environmental Observatory Bottle Chemistry data. This data set includes diverse measurements of seawater chemistry along with supporting conductivity, temperature, and depth (CTD) data from the Arctic Ocean near the North Pole.

# Setup
```{r, load packages}
#| warning: false
#| message: false
library(readr)
library(here)
```

## Read in data
```{r, read in data}
#| message: false
#| warning: false
bg_chem <- read_csv(here::here("data/BGchem2008data.csv"))
```

# Analysis

```{r, explore data}
#| eval: false
#| echo: false
colnames(bg_chem)
str(bg_chem)
head(bg_chem)
summary(bg_chem)
```

## Summary statistics
```{r, mean variables}
nitrate <- mean(bg_chem$NO3)
nitrate
nitrite <- mean(bg_chem$NO2)
nitrite
amm     <- mean(bg_chem$NH4)
amm
phos    <- mean(bg_chem$P)
phos
```

## Redfield ratio
```{r, redfield ratio}
ratio <- (nitrate + nitrite + amm) / phos
ratio
```

The Redfield ratio for this dataset is approximately `{r} round(ratio)`.

## Plot
```{r, plot}
plot(bg_chem$P, bg_chem$NO2 + bg_chem$NO3 + bg_chem$NH4)
```

# Conclusion
